European or American? A re-examination of the transatlantic influence over the IMF

### 2025-04-22 demo/demo.qmd
use project dir as wd
Change subtitle
add name placeholders

---
title: European or American? A re-examination of the transatlantic influence over the IMF
# subtitle: GV499 Dissertation
header-includes: |
  \AtBeginDocument{\title[GV499 Dissertation]{European or American? A re-examination of the transatlantic influence over the IMF}}
date: last-modified
author: Dianyi Yang
format:
  beamer:
    theme: Madrid
bibliography: references.bib
csl: extra/apa.csl
---

@@

```{r results}
load('../save/regtable.RData')

>>>>

---
title: European or American? A re-examination of the transatlantic influence over the IMF
header-includes: |
  \AtBeginDocument{\title[European or American]{European or American? A re-examination of the transatlantic influence over the IMF}}
date: last-modified
author:
- name: Dianyi Yang
# - name: Tong Hu // name placeholders subject to change
# - name: Zhenyi Chen
format:
  beamer:
    theme: Madrid
bibliography: references.bib
csl: extra/apa.csl
---

@@

```{r results}
load('save/regtable.RData')
